In-silico molecular enrichment and clearance of the human intracranial space

### 2025-01-06 paper/supplementary_main.tex
fix figure paths

Considering the mean tracer concentrations in the CSF, parenchyma and arterial and venous PVS domain over the first 24\,h after injection, we observe negligible changes with both mesh and time refinement (\cref{fig:mesh_convergence_concentrations} and 
\ref{fig:time_convergence_concentrations}). In addition, we compute the mean and maximum enhancement factor, the maximum CSF pressure and velocity in both the cardiac-driven and CSF production-induced flow fields, and mean concentrations at 3, 6, 12 and 24\,h for all mesh resolutions and time steps (\cref{fig:mesh_convergence} and \cref{fig:time_convergence}). While the maximum dispersion factor increases by about 60\,\% from the coarse to the standard mesh, it stabilizes with the next refinement step. All other quantities change with less than 10\,\% with mesh refinement, and less than 1\,\% with time refinement. We thus conclude that the standard resolution mesh and a time step of $dt=120\,$s offers sufficient accuracy for our simulations.

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{paper/figures/mesh_refinement.png}
    \caption{Illustration of the three different meshes: low resolution, standard resolution, high resolution (from left to right).}
    \label{fig:mesh_refinement}
\end{figure}

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width = 1 \linewidth]{figures/mesh_refinement_par_csf_mean.png}
        \caption{Mean tracer concentration in CSF and parenchyma under mesh refinement}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
     \includegraphics[width= 1 \linewidth]{figures/mesh_refinement_art_ven_mean.png}
         \caption{Mean tracer concentration in PVSs around (veins and) arteries  under mesh refinement}
    \end{subfigure}
    \caption{Mean tracer concentrations over the first 24\,h after injection on the CSF and parenchyma (a), and the arterial and venous PVS (b) computed on the LowRes, standard and HighRes meshes with a timestep of $dt=120$\,s.}
    \label{fig:mesh_convergence_concentrations}
\end{figure}

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics[trim={0.5cm 1cm 0.05cm 0.8cm}, clip, width = 1.05 \linewidth]{figures/mesh_refinement.pdf}
        \caption{Convergence of key quantities of interest with mesh refinement}
        \label{fig:mesh_convergence}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
     \includegraphics[trim={0.5cm 1cm 0.05cm 0.8cm}, clip,width= 1.05 \linewidth]{figures/time_refinement.pdf}
        \caption{Convergence of key quantities of interest with time refinement}
        \label{fig:time_convergence}
    \end{subfigure}
    \caption{minimal ($\rm h_{min}$) and maximal ($\rm h_{max}$) mesh cell sizes (computed as cell circumradius $\times 2$) (A); number of points and tetrahedral cells in each mesh (B); mean dispersion enhancement factor $R$ (C), maximum dispersion enhancement factor $R$ (D); maximum pressure in steady CSF production flow (E), maximum pressure in cardiac-driven CSF flow (F); maximum CSF velocity in steady CSF production flow (G); maximum CSF velocity in cardiac-driven CSF flow (H);  mean tracer concentration in the CSF, parenchyma, arterial PVS and venous PVS at 3,6,12 and 24\,h (I, J, K and L).}
\end{figure}

@@

>>>>

Considering the mean tracer concentrations in the CSF, parenchyma and arterial and venous PVS domain over the first 24\,h after injection, we observe negligible changes with both mesh and time refinement (\cref{fig:mesh_convergence_concentrations} and 
\ref{fig:time_convergence_concentrations}). In addition, we compute the mean and maximum enhancement factor, the maximum CSF pressure and velocity in both the cardiac-driven and CSF production-induced flow fields, and mean concentrations at 3, 6, 12 and 24\,h for all mesh resolutions and time steps (\cref{fig:mesh_convergence} and \cref{fig:time_convergence}). While the maximum dispersion factor increases by about 60\,\% from the coarse to the standard mesh, it stabilizes with the next refinement step. All other quantities change with less than 10\,\% with mesh refinement, and less than 1\,\% with time refinement. We thus conclude that the standard resolution mesh and a time step of $dt=120\,$s offers sufficient accuracy for our simulations. In addition, we compute the standard model without allowing tracer transport across the models outer boundary, confirming mass conservation of our numerical scheme (\cref{fig:mass_conservation}).

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{figures/mesh_refinement.png}
    \caption{Illustration of the three different meshes: low resolution, standard resolution, high resolution (from left to right).}
    \label{fig:mesh_refinement}
\end{figure}

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width = 1 \linewidth]{figures/csf_minmax.png}
        \caption{Minimum and maximum tracer concentration in  the CSF under mesh refinement}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
     \includegraphics[width= 1 \linewidth]{figures/par_minmax.png}
        \caption{Minimum and maximum tracer concentration in the parenchyma under mesh refinement}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width = 1 \linewidth]{figures/art_minmax.png}
        \caption{Minimum and maximum tracer concentration in PVSs around arteries under mesh refinement}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
     \includegraphics[width= 1 \linewidth]{figures/ven_minmax.png}
         \caption{Minimum and maximum tracer concentration in PVSs around veins under mesh refinement}
    \end{subfigure}
    \caption{Minumum and maximum tracer concentrations over the first 24\,h after injection on the CSF and parenchyma (a), and the arterial and venous PVS (b) computed on the LowRes, standard and HighRes meshes with a timestep of $dt=120$\,s.}
    \label{fig:mesh_convergence_concentrations}
\end{figure}

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics[trim={0.5cm 1cm 0.05cm 0.8cm}, clip, width = 1.05 \linewidth]{figures/modelALowRes_modelA_modelAHighRes.pdf}
        \caption{Convergence of key quantities of interest with mesh refinement}
        \label{fig:mesh_convergence}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
     \includegraphics[trim={0.5cm 1cm 0.05cm 0.8cm}, clip,width= 1.05 \linewidth]{figures/modelAsmalldt_modelA_modelAlargedt.pdf}
        \caption{Convergence of key quantities of interest with time refinement}
        \label{fig:time_convergence}
    \end{subfigure}
    \caption{minimal ($\rm h_{min}$) and maximal ($\rm h_{max}$) mesh cell sizes (computed as cell circumradius $\times 2$) (A); number of points and tetrahedral cells in each mesh (B); mean cardiac dispersion enhancement factor $R$ (C), maximum cardiac dispersion enhancement factor $R$ (D); maximum pressure in steady CSF production flow (E), maximum pressure in cardiac-driven CSF flow (F); maximum CSF velocity in steady CSF production flow (G); maximum CSF velocity in cardiac-driven CSF flow (H);  mean tracer concentration in the CSF, parenchyma, arterial PVS and venous PVS at 3,6,12 and 24\,h (I, J, K and L).}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{figures/modelAMassConservation_total_conc.png}
    \caption{total tracer content in CSF, parenchyma and arterial and venous PVS for the standard model without tracer outflow, illustrating numerical mass conservation.}
    \label{fig:mass_conservation}
\end{figure}
